``FISTA'' in Banach spaces with adaptive discretisations

### 2021-09-07 response.tex

	\todo{I'm not sure what is being requested here. Is he asking for another numerical example? We could change the data fidelity for the Wavelet example quite easily? I'm actually struggling to think of another common smooth data fidelity which isn't Entropy-smoothed OT...}

	\item \review{page 17, line 28: missing word? ``most require''?}

	Thank you for noticing this mistake.

	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}

@@

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity. The old Figure 2 only plotted the discrete gap which showed convergence to stationarity rather than necessarily an `accurate solution'. If we measure accuracy in terms of the continuous gap (the value 0.1 in this case), you are correct that the nonadaptive scheme reaches high precision for the set accuracy level. In practice, this may mean that the adaptive reconstruction has more values which are approximately but not exactly 0.

	\todo{What point is being made here? Have they just been confused about different `accuracy' metrics in the two plots? Should I add a comment on precision in the text?}
\end{enumerate}

### 2021-09-07 paper.tex
Typos and updated figures

\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\renewcommand{\sfrac}[2]{\,^{#1}\!\!/\!_{#2}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\newcommand{\1}{\F{1}}
\DeclareMathOperator{\st}{\;s.t.\;}
\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}

@@

	\begin{abstract}
		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the optimisation domain is contained in a suitable Hilbert space. We propose a modified algorithm where each iteration is performed in a subspace, and that subspace is allowed to change at every iteration. Analytically, this allows us to guarantee convergence in a Banach space setting, although at a reduced rate depending on the conditioning of the specific problem. Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.
	\end{abstract}
	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}

@@

	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
	\begin{itemize}
		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{the minimum is not achieved. For example, in Lasso discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
		\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
	\end{itemize}
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty. Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations. The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$. The permitted refinement steps are also more broad in our work.

	\subsection{Outline}
	This chapter is organised as follows. Section~\ref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, Algorithm~\ref{alg: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}. The main results are Theorems~\ref{thm: exponential FISTA convergence}/~\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.

	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\varf0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\varf0^*$}{the minimiser}. The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.

@@

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining }{closed }subspaces $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{classical} algorithm.

@@

	The precise constants associated to a given rate are given in the statements of the theorems but, for convenience, are otherwise omitted from the text. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will use the notation:
	\begin{align*}
		a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
		\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
	\end{align*}
	\edit{}{For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
	\begin{equation}
		\Norm{\partial\op{E}(\varf0)} \coloneqq \inf_{\varf1\in\partial\op{E}(\varf0)}\Norm{\varf1}
	\end{equation}
	for any norm $\Norm\cdot$.}

@@

	\paragraph{Step 1: Quantifying the stability}
	\begin{adaptiveStep}\label{step: step 1 stability}
		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$. In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that 
		\begin{equation}\label{eq: mini FISTA convergence}
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
		\end{equation}
		for $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$. The similarities to \eqref{eq: classical FISTA} are clear. If $\spcf0^n=\spcf0$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0}$ and the two estimates agree. These extra terms quantify the robustness to changing of discretisation.
	\end{adaptiveStep}

@@

	\paragraph{Step 5: Sufficiently slow refinement}
	\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate. If the subspaces refine too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence. If the resolution is too coarse then we are overfitting to the discrete minimiser, but if the resolution is too fine then convergence of the energy is slow. Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of 
		$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\op{E}}$. In particular, if \edit{$\varf0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
	\end{adaptiveStep}

@@

		Spatial adaptivity is robust, so long as the scaling properties of Step~\ref{step: step 2 smoothness} are satisfied. The only other constraint is to ensure that the partial telescoping of Step~\ref{step: step 3 convergence bound} still holds. Lemma~\ref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
		$$\edit{}{\varf0_{n_k-1}}\in\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
		Convergence is most stable if the approximation spaces $\spcf0^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.

@@

	\begin{theorem}[\edit{}{analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}}]\label{thm: mini FISTA convergence}
		\Copy{thm: mini FISTA convergence}{
			Fix a sequence of subspaces $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$. Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}. 
			Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
		}
		\begin{equation}\label{eq: FISTA inequality}\Copy{thm:eq: mini FISTA convergence}{
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
		}\end{equation}
	\end{theorem}
	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}. This result is the key approximation for showing convergence of FISTA with refining subspaces. In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.

	\edit{The}{If there exists a minimiser $\varf0^*\in\argmin_{\varf0\in\F H}\op{E}(\varf0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\tens{\Pi}_n\varf0^*$, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\varf0^*)=\infty$ and so this inequality becomes useless. For example, if $\op{f}(\varf0) = \norm{\varf0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$, and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$. On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then 
	$$\tens{\Pi}_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\sfrac\meshsize2.$$
	In particular $\tens{\Pi}_n\varf0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\varf0^*) = \infty$. The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly. The penalty for this flexibility is a more complicated analysis, each time the subspace changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.

@@

	\subsection{Refinement without overfitting}
	The aim of Step~\ref{step: step 4 sufficiently fast} is to show that $n$ iterations of Algorithm~\ref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\spcf0^n$. In other words, we would like to ensure that
	\begin{equation}
		\op{E}(\varf0_n) - \min_{\varf0\in\spcf0^n}\op{E}(\varf0) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)}^2}{n^2}
	\end{equation}
	uniformly in $n$. If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subspaces. This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\spcf0}$. Combining the assumptions given by Definition~\ref{def: exp subspaces} and the result of Lemma~\ref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of Algorithm~\ref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e. $\spcf0^n$ grows sufficiently quickly).

@@

	\noindent The proof is given in Lemma~\ref{app:thm: sufficiently fast}. We make two observations of the optimality of Lemma~\ref{thm: sufficiently fast}:
	\begin{itemize}
		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\spcf0^N$ is 
		$$ \op{E}_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\op{E}(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\op{E}_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\op{E}}^{-K}.$$
		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
		\item If $\spcf0$ is finite dimensional, then the $\vars3_{\Varf0}=1$ is almost trivially satisfied. Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e. the sums over $k$ are finite). 
	\end{itemize}

@@

	\subsection{Continuous case}\label{sec: continuous lasso rate}
	We start by estimating rates in the case $\spcf0=\C M(\Domain)$ where $\Domain =[0,1]^d$. In this case we choose $\tilde{\spcf0}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e. $\meshsize=\sfrac12$).

>>>>

\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\newcommand{\1}{\F{1}}
\DeclareMathOperator{\st}{\;s.t.\;}
\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}

@@

	\begin{abstract}
		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the \edit{optimisation domain}{optimiser} is contained in a suitable Hilbert space. We propose a modified algorithm where each iteration is performed in a subspace, and that subspace is allowed to change at every iteration. Analytically, this allows us to guarantee convergence in a Banach space setting, although at a reduced rate depending on the conditioning of the specific problem. Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.
	\end{abstract}
	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}

@@

	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
	\begin{itemize}
		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved. For example, in Lasso discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
		\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
	\end{itemize}
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty. Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations. The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$. The permitted refinement steps are also more broad in our work.

	\subsection{Outline}
	This work is organised as follows. Section~\ref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, Algorithm~\ref{alg: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}. The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.

	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} \edit{}{in Banach spaces }and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\varf0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\varf0^*$}{the minimiser}. The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.

@@

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining }{closed }subspaces $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.

@@

	The precise constants associated to a given rate are given in the statements of the theorems but, for convenience, are otherwise omitted from the text. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will use the notation:
	\begin{align*}
		a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
		\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
	\end{align*}
	\edit{}{For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
	\begin{equation}
		\Norm{\partial\op{E}(\varf0)} \coloneqq \inf_{\varf1\in\partial\op{E}(\varf0)}\Norm{\varf1}
	\end{equation}
	for any specified norm $\Norm\cdot$.}

@@

	\paragraph{Step 1: Quantifying the stability}
	\begin{adaptiveStep}\label{step: step 1 stability}
		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$. In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that 
		\begin{equation}\label{eq: mini FISTA convergence}
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
		\end{equation}
		for any $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$. The similarities to \eqref{eq: classical FISTA} are clear. If $\spcf0^n=\edit{\spcf0}{\F H}$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the two estimates agree. These extra terms quantify the robustness to changing of discretisation.
	\end{adaptiveStep}

@@

	\paragraph{Step 5: Sufficiently slow refinement}
	\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate. If the subspaces refine too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence. If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow. Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of 
		$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\op{E}}$. In particular, if \edit{$\varf0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
	\end{adaptiveStep}

@@

		Spatial adaptivity is robust, so long as the scaling properties of Step~\ref{step: step 2 smoothness} are satisfied. The only other constraint is to ensure that the partial telescoping of Step~\ref{step: step 3 convergence bound} still holds. Lemma~\ref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
		$$\edit{}{\varf0_{n_k-1}\in}\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
		Convergence is most stable if the approximation spaces $\spcf0^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.

@@

	\begin{theorem}[\edit{}{analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}}]\label{thm: mini FISTA convergence}
		\Copy{thm: mini FISTA convergence}{
			Fix a sequence of subspaces $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$. Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
		}
		\begin{equation}\label{eq: FISTA inequality}\Copy{thm:eq: mini FISTA convergence}{
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
		}\end{equation}
	\end{theorem}
	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}. This result is the key approximation for showing convergence of FISTA with refining subspaces. In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.

	\edit{The}{If there exists a minimiser $\varf0^*\in\argmin_{\varf0\in\F H}\op{E}(\varf0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\tens{\Pi}_n\varf0^*$, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\varf0^*)=\infty$ and so this inequality becomes useless. For example, if $\op{f}(\varf0) = \norm{\varf0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$, and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$. On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then 
	$$\tens{\Pi}_n\varf0^*\left(\varx0_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\tfrac\meshsize2.$$
	In particular $\tens{\Pi}_n\varf0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\varf0^*) = \infty$. The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly. The penalty for this flexibility is a more complicated analysis, each time the subspace changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.

@@

	\subsection{Refinement without overfitting}
	The aim of Step~\ref{step: step 4 sufficiently fast} is to show that $n$ iterations of Algorithm~\ref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\spcf0^n$. In other words, we would like to ensure that
	\begin{equation}
		\op{E}(\varf0_n) - \min_{\varf0\in\spcf0^n}\op{E}(\varf0) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)}^2}{n^2}
	\end{equation}
	uniformly in $n$. If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subspaces. This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\F H}$. Combining the assumptions given by Definition~\ref{def: exp subspaces} and the result of Lemma~\ref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of Algorithm~\ref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e. $\spcf0^n$ grows sufficiently quickly).

@@

	\noindent The proof is given in Lemma~\ref{app:thm: sufficiently fast}. We make two observations of the optimality of Lemma~\ref{thm: sufficiently fast}:
	\begin{itemize}
		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\spcf0^N$ is 
		$$ \op{E}_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\op{E}(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\op{E}_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\op{E}}^{-K}.$$
		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
		\item If $\edit{\spcf0}{\F H}$ is finite dimensional, then the $\vars3_{\Varf0}=1$ is almost trivially satisfied. Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e. the sums over $k$ are finite). 
	\end{itemize}

@@

	\subsection{Continuous case}\label{sec: continuous lasso rate}
	We start by estimating rates in the case $\spcf0=\C M(\Domain)$ where $\Domain =[0,1]^d$. In this case we choose $\tilde{\spcf0}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e. $\meshsize=\tfrac12$).
